### 2020-07-16 article.tex
Three suggested changes, fix broken URL, and several typos

The rest of the operations are then performed directly inside HPDDM.
Specifically, within Krylov methods using the Arnoldi process, or when recycling is requested,
one has to compute $QR$ factorizations of tall-and-skinny dense matrices to orthonormalize
candidate basis vectors. Such operations are performed using the CholQR algorithm~\cite{stathopoulos2002block}, or
via the block variants of the (modified) Gram--Schmidt method.
For Hessenberg matrices generated by the Arnoldi
process, it is common to update their $QR$ decomposition using Givens
rotations~\cite{saad2003iterative}. For block Hessenberg matrices, Householder reflectors are
used instead~\cite{gutknecht2008updating}.
These orthonormalization variants can selected at runtime with the option \pk{-ksp\_hpddm\_qr (cholqr$|$mgs$|$cgs)}. {\color{red} API?}

@@

With these added functions, it is now possible to do code refactorization for
applications that deal with multiple right-hand sides.  As a striking example,
LOBPCG~\cite{knyazev2001toward} or CISS~\cite{sakurai2003projection}
implementations in SLEPc~\cite{hernandez2005ssf}, the Scalable Library for
Eigenvalue Problem computations built on top of PETSc, were previously not
using blocking.  It has been rewritten for version 3.14.0 and the benefits of
this new implementation is displayed~\cref{sec:lobpcg}.

@@

In this section, we apply recycling Krylov methods in the context linear
stability analysis and consider the solution the following generalized eigenvalue problem:

@@

There are different methods to compute the eigenvalues
of~\cref{eq:lsa} near a complex-valued shift $\sigma$. In this paragraph, emphasis will be put
on Krylov--Schur methods~\cite{Stewart2002}, which rely on spectral transformations
and on the solution of successive linear systems such as:
\begin{equation}\label{eq:ks}
    \left(J(q_b) - \sigma \begin{bmatrix}M&0\\0&0\end{bmatrix}\right)x_i = b_i,
\end{equation}
which, in SLEPc, are parameterized using the \pk{-st\_} prefix.
In this work, the above linear system is preconditioned using a modified augmented Lagrangian
approach~\cite{Benzi2011a,moulin2018al}

@@

The Krylov--Schur algorithm converges in six outer iterations.

@@

They can be reproduced by using the mini-app \url{http://jolivet.perso.enseeiht.fr/MatProduct.c} and any input \pk{MatAIJ} stored in binary format,

@@

    \item with a block size of 1, top plot $b=1$ in~\cref{fig:perfAX}, using any type but \pk{MatAIJ}~\ref{pgfplots:aij1} is counterproductive when $N>1$, see~\ref{pgfplots:baij1} and~\ref{pgfplots:sbaij1}, even when using MKL, see~\ref{pgfplots:mklbaijseq1} and~\ref{pgfplots:mklsbaijseq1}. With 8 or more columns, the performance of \pk{MatAIJ} plateaus and the efficiency reaches approximately 200\%, while the performance of the MKL primitives stagnate at around 175\% see~\ref{pgfplots:aij1};

@@

The mini-app is then used to benchmark intranode performance of matrix--matrix multiplications, either with multiple OpenMP threads, or by offloading the operation to a GPU and use cuSPARSE~\cite{cusparse-web-page} as interfaced in PETSc.

@@

\pk{MatAIJMKL} with $N=1$ but different numbers of threads is also reported

@@

and $N=64$, right-most middle plot in~\cref{fig:perfAXpar}, with approximately

@@

and $N=64$, right-most bottom plot in~\cref{fig:perfAXpar}, performs at around

>>>>

The rest of the operations are then performed directly inside HPDDM.
Specifically, within Krylov methods using the Arnoldi process, or when recycling is requested,
one has to compute $QR$ factorizations of tall-and-skinny dense matrices to orthonormalize
candidate basis vectors. Such operations are performed using the CholQR algorithm~\cite{stathopoulos2002block}, or
via the block variants of the (modified) Gram--Schmidt method.
For Hessenberg matrices generated by the Arnoldi
process, it is common to update their $QR$ decomposition using Givens
rotations~\cite{saad2003iterative}. For block Hessenberg matrices, Householder reflectors are
used instead~\cite{gutknecht2008updating}.
These orthonormalization variants can be selected at runtime with the option \pk{-ksp\_hpddm\_qr (cholqr$|$mgs$|$cgs)}. {\color{red} API?}

@@

With these added functions, it is now possible to do code refactorization for
applications that deal with multiple right-hand sides.  As a striking example,
LOBPCG~\cite{knyazev2001toward} or CISS~\cite{sakurai2003projection}
implementations in SLEPc~\cite{hernandez2005ssf}, the Scalable Library for
Eigenvalue Problem computations built on top of PETSc, were previously not
using blocking when applying the preconditioner or solving linear systems. This has been rewritten for version 3.14.0 and the benefit of
this new implementation is displayed in~\cref{sec:lobpcg}.

@@

In this section, we apply recycling Krylov methods in the context of linear
stability analysis and consider the solution of the following generalized eigenvalue problem:

@@

There are different methods to compute the eigenvalues
of~\cref{eq:lsa} near a complex-valued shift $\sigma$. In this paragraph, emphasis will be put
on the Krylov--Schur method~\cite{Stewart2002}, which for interior eigenvalues relies on spectral transformations
and on the solution of successive linear systems such as:
\begin{equation}\label{eq:ks}
    \left(J(q_b) - \sigma \begin{bmatrix}M&0\\0&0\end{bmatrix}\right)x_i = b_i,
\end{equation}
which, in SLEPc, are parameterized using the \pk{-st\_} prefix.
In this work, the above linear system is preconditioned using a modified augmented Lagrangian
approach~\cite{Benzi2011a,moulin2018al}

@@

The Krylov--Schur algorithm converges in six outer iterations (restarts), with a total of 46 inner solves~\cref{eq:ks}.

@@

They can be reproduced by using the mini-app \url{https://github.com/prj-/jolivet2020petsc/blob/master/MatProduct.c} and any input \pk{MatAIJ} stored in binary format,

@@

    \item with a block size of 1, top plot $b=1$ in~\cref{fig:perfAX}, using any type but \pk{MatAIJ}~\ref{pgfplots:aij1} is counterproductive when $N>1$, see~\ref{pgfplots:baij1} and~\ref{pgfplots:sbaij1}, even when using MKL, see~\ref{pgfplots:mklbaijseq1} and~\ref{pgfplots:mklsbaijseq1}. With 8 or more columns, the performance of \pk{MatAIJ} plateaus and the efficiency reaches approximately 200\%, while the performance of the MKL primitives stagnate at around 175\%, see~\ref{pgfplots:aij1};

@@

The mini-app is then used to benchmark intranode performance of matrix--matrix multiplications, either with multiple OpenMP threads, or by offloading the operation to a GPU and using cuSPARSE~\cite{cusparse-web-page} as interfaced in PETSc.

@@

\pk{MatAIJMKL} with $N=1$ but different numbers of threads is also reported in

@@

and $N=64$, rightmost middle plot in~\cref{fig:perfAXpar}, with approximately

@@

and $N=64$, rightmost bottom plot in~\cref{fig:perfAXpar}, performs at around
